Is There a Correlation Between Preference and Perceptions of Inaction and Action in Decision-Making and Gender? An Analysis of Evaluations of Actions and Inaction Decision-makers in Risky Decisions Resulting in Negative Outcomes Study 2.

### 2024-02-15 outputs/paper/paper.qmd
paper update

## read in cleaned data 
data_gender = read_csv(
  file = "~/Preference-and-Perception-of-Decision-Making/outputs/data/00-cleaned_study_2_data.csv",
  show_col_types = FALSE
)

>>>>

## Read in cleaned data 
data_gender = read_csv(
  file = "~/Preference-and-Perception-of-Decision-Making/outputs/data/00-cleaned_study_2_data.csv",
  show_col_types = FALSE
)
